An Open-Source Repository of Real-Time COVID-19 Indicators

### 2021-06-12 indicators/paper/paper.tex
Sig statement is exactly 120 words

% Please add a significance statement to explain the relevance of your work
\significancestatement{To properly study the COVID-19 pandemic, its effects on
  society, and measures for reducing its spread, researchers need detailed data
  on the course of the pandemic. Standard public health data streams suffer
  inconsistent reporting and frequent, unexpected revisions. They also miss some
  important aspects worthy of study, such as certain aspects of public
  behavior. We present an open database of COVID signals in the United States,
  measured primarily at the county level and updated daily. These include
  traditionally reported COVID cases and deaths, but also many others: signals
  based on measures of mobility, social distancing behaviors, internet search
  trends, self-reported symptoms, and patterns COVID-related activity in
  de-identified medical insurance claims. The database provides all signals in a
  common, easy-to-use format, empowering both public health research and
  operational decision-making.
}

>>>>

% Please add a significance statement to explain the relevance of your work
\significancestatement{To study the COVID-19 pandemic, its effects on society,
  and measures for reducing its spread, researchers need detailed data on the
  course of the pandemic. Standard public health data streams suffer
  inconsistent reporting and frequent, unexpected revisions. They also miss
  other aspects of a population's behavior, worthy of consideration. We
  present an open database of COVID signals in the United States, measured at
  the county level and updated daily. These include traditionally reported COVID
  cases and deaths, and many others: signals based on measures of mobility,
  social distancing, internet search trends, self-reported symptoms, and
  patterns COVID-related activity in de-identified medical insurance claims. The
  database provides all signals in a common, easy-to-use format, empowering both
  public health research and operational decision-making.
}
